Selection of Polynomial Features by Genetic Algorithms

### 2013-07-19 tests_Housing.Rmd
change Pictures, clean folder

########################################################

>>>>

########################################################
# check what attributes Random Forest select has the most importants

train.p.size <- 0.7 # percentage of training set
n.vars       <- ncol(my.data)-1

inTrain   <- sample(1:nrow(my.data), train.p.size * nrow(my.data))
train.set <- my.data[inTrain,]
test.set  <- my.data[-inTrain,]

rf.model <- randomForest(y ~ ., data=train.set, importance=TRUE, do.trace=100, ntree=100)
rf.model$importance

### 2013-07-19 tests_test.Rmd
change Pictures, clean folder

source("gapolyfuncs.R")
report <- make.report(my.data, population=100, iterations=50, mutation.rate=0.05)

@@

# df <- data.frame(GA.Poly = report$ga.error,
#                  Lin.Reg = report$lm.error,
#                  SVM = report$svm.error,
#                  RPART = report$rpart.error,
#                  Rnd.For = report$rf.error,
#                  CI.Tree = report$citree.error)
# 
# write.table(df, "Articial_dataset.txt")

>>>>

source("gapolyfuncs.R")
report <- make.report(my.data, population=100, iterations=50, mutation.rate=0.15)

@@

df <- data.frame(GA.Poly = report$ga.error,
                 Lin.Reg = report$lm.error,
                 SVM = report$svm.error,
                 RPART = report$rpart.error,
                 Rnd.For = report$rf.error,
                 CI.Tree = report$citree.error)

write.table(df, "Articial_dataset.txt")

### 2013-07-19 texts/paper-draft.tex
change Pictures, clean folder

\ac{GA} where, arguably, one the hottest topics of research in the recent decades and with good reason since they outline an optimization scheme easy to conceptualize and with very broad application. If a nonlinear (or otherwise) model requires parameterization, \acp{GA} provide a simple and often effective approach to search for locally optimal parameters. Research related to genetic algorithms abound and spans from the 1950s seminal work of Nils Aall Barricelli \cite{barricelli1962numerical} in the Institute for Advanced Study of Princeton to today's principal area of study for thousands of researchers, covered in hundreds of conferences, workshops and other meetings. Perhaps the key impulse to \acp{GA} come from John Holland's work and his book ``Adaptation in Natural and Artificial Systems'' \cite{holland1975adaptation}.

@@

The chromosome coding will as follow:
\begin{enumerate}
\item an initial segment detailing which monomials are active (the 1st monomial is always active), these are represented in unary description
\item the chromosome is split into $m$ sets of bits of equal size 
  (a monomial)
\item each monomial is split into $n$ sets of $d$ size each, i.e., a variable
\item for each variable, the remaining bits give the binary description of the variable degree, i.e., the maximum exponent is given by $2^d-1$
\end{enumerate}

Eg: consider polynomial $x_1^3 x_3 + x_3^7 + x_1 x_2$ with $m = 4, n = 3$ and $d=3$. One possible encoding would be:
$$110 - 011,000,001~~;~~000,000,111~~;~~001,001,000~~;~~110,010,101$$

@@

The first $3$ bits inform that the second and third monomials are active while the fourth is not (as said, the first monomial is always active). This last monomial does not enter neither in the polynomial regression nor in the fitness evaluation. However, it acts as a kind of junk DNA, becoming active when the third bit of the entire sequence flips from 0 to 1.

Let's interpret the first monomial description, $011,000,001$. It is divided by three since $n=3$. The first triple $011$ is the binary description of the exponent of variable $x_1$ which is 3, so the first monomial includes $x_1^3$. The second triple, $000$, means that $x_2$ is not part of the monomial. The third triple $001$ says that variable $x_3$ has exponent $1$, so the first monomial consists of $x_1^3 x_3$. All the remaining sets of $9$ bits are interpreted the same way and we get the previous polynomial.

Notice that all binary descriptions give rise to valid polynomials. However, if the coding consists of entirely zeros, by convention, it describes polynomial $x_1$. This has to do with the execution of the polynomial regression that would fail if we interpret it as the zero polynomial. Anyway, for progressive larger  binary descriptions, the chances of getting this zero description decrease exponentially, so it does not impact in any meaningful way in the algorithm's performance.

@@

Somewhat unexpectedly after some experiences it was found that lower values for $\lambda$ sometimes provide better, even if marginal, results. Figure~\ref{Abalone_dataset_lambdas} shows results for the Abalone dataset with five runs for each $\lambda$ (cf. Experimental Results includes information about these datasets).

@@

\end{axis}
\end{tikzpicture}
\includegraphics[height=6cm,width=\textwidth,angle=0]{figures/Abalone_dataset_lambdas.eps}

\caption{Fitness progress for the Abalone dataset.}\label{Abalone_dataset_lambdas}

@@

%\begin{figure}[htb]
%	\begin{center}
%		\includegraphics[height=6cm,width=10cm,angle=0]
%			{figures/Abalone_dataset_lambdas.eps}
%		\caption{fitness progress for Abalone dataset}
%		\label{Abalone_dataset_lambdas}
%	\end{center}
%\end{figure}

Figure~\ref{Auto-Mpg_dataset_lambdas} presents regularization results for the Auto-MPG dataset:

\begin{figure}[htb]
	\begin{center}
		\includegraphics[height=6cm,width=10cm,angle=0]
			{figures/Auto-Mpg_dataset_lambdas.eps}
		\caption{fitness progress for Abalone dataset}
		\label{Auto-Mpg_dataset_lambdas}
	\end{center}
\end{figure}

The typical inflection point is around $\lambda = 0.8$. We'll use the regularisation parameter with this value.

@@

\emph{Define the genetic operators}

\subsection{Other Search Parameters}

\emph{Explain the remaining search parameters}

@@

To compare this paper's algorithm we applied the exact same train and test samples with other learning algorithms, namely: Linear Regression, Support Vector Machines~\cite{Meyer12}, Regression Trees~\cite{Therneau13}, Conditional Inference Trees~\cite{Hothorn06, Strobl07, Strobl08} and Random Forests~\cite{Liaw02}

In order to train and test the performance of \ac{GAPoly} it was used several datasets (see below). For each dataset, we selected 70\% for training purposes and the remaining observations to make the test set in order to compute the estimated \ac{rmse}. To achieve more robust results, for most datasets there were 25 runs, each one with different samples for the train and test sets. For the datasets with attribute values of different magnitudes, a preliminary scaling was executed. The results below are boxplots for the test set error predictions over these different runs.

\textbf{Artificial}: this is an artificial dataset with four numeric features, $x_1, \ldots x_4$, where $x_1,x_3$ are outcomes from Poisson random variables, and $x_2,x_4$ from Normal random variables. The dependent variable $y$ is given by expression $x_2x_4^2 + x_1^2x_3 + 5$. The dataset includes 50 observations.

\begin{figure}[htb]
	\begin{center}
		\includegraphics[height=6cm,width=10cm,angle=0]
			{figures/artificial_dataset1_lambda1_0.eps}
		\caption{results for Artificial dataset}
		\label{artificial_dataset1_lambda1.0}
	\end{center}
\end{figure}

This dataset was used in order to verify if \ac{GAPoly} was able to find the polynomial relation, which the algorithm did (cf. figure~\ref{artificial_dataset1_lambda1.0}). In this case, all runs used a population of 100 with 50 iterations for each run.

@@

\textbf{Housing}: This data set concerns the task of predicting housing values in areas of Boston. There are 13 continuous attributes and the dependent variable is the median value of owner-occupied homes in \$1000's\footnote{This and the remaining regression datasets were selected from Luis Torgo's data repository, http://www.dcc.fc.up.pt/~ltorgo/Regression/DataSets.html. Most of these set originally come from UCI ML repository, http://archive.ics.uci.edu/ml/}. There are 506 observations. Figure~\ref{Housing_dataset_lambda0.8_25runs} presents the results for this dataset.

\begin{figure}[htb]
	\begin{center}
		\includegraphics[height=6cm,width=10cm,angle=0]
			{figures/Housing_dataset_lambda0_8_25runs.eps}
		\caption{results for Boston Housing dataset}
		\label{Housing_dataset_lambda0.8_25runs}
	\end{center}
\end{figure}

Just as an example of the model the \ac{GAPoly} algorithm outputs: in this dataset the best polynomial, with a \ac{rmse} of 0.38 for the test set, was the following:

@@

@@

\begin{figure}[htb]
	\begin{center}
		\includegraphics[height=6cm,width=10cm,angle=0]
			{figures/Abalone_dataset_lambda0_8_25runs.eps}
		\caption{results for Abalone dataset}
		\label{Abalone_dataset_lambda0.8_25runs}
	\end{center}
\end{figure}

@@

\begin{figure}[htb]
	\begin{center}
		\includegraphics[height=6cm,width=10cm,angle=0]
			{figures/Auto-Mpg_dataset_lambda0_8_25runs.eps}
		\caption{results for Auto-MPG dataset}
		\label{Auto-Mpg_dataset_lambda0.8_25runs}
	\end{center}
\end{figure}

@@

\begin{figure}[htb]
	\begin{center}
		\includegraphics[height=6cm,width=10cm,angle=0]
			{figures/Kinematics300_lambda0_8_25runs.eps}
		\caption{results for Kinematics dataset}
		\label{Kinematics300_lambda0.8_25runs}
	\end{center}
\end{figure}

@@

\subsection{Discussion}

The proposed method has competitive results comparing with some well-known regression methods. Only Random Forest outperforms \ac{GAPoly} systematically (it outperforms all the others) except in the Auto-MPG test and, of course, in the artificial dataset that uses a straightforward polynomial relation.

>>>>

\ac{GA} where, arguably, one of the hottest topics of research in the recent decades and with good reason since they outline an optimization scheme easy to conceptualize and with very broad application. If a nonlinear (or otherwise) model requires parameterization, \acp{GA} provide a simple and often effective approach to search for locally optimal parameters. Research related to genetic algorithms abound and spans from the 1950s seminal work of Nils Aall Barricelli \cite{barricelli1962numerical} in the Institute for Advanced Study of Princeton to today's principal area of study for thousands of researchers, covered in hundreds of conferences, workshops and other meetings. Perhaps the key impulse to \acp{GA} come from John Holland's work and his book ``Adaptation in Natural and Artificial Systems'' \cite{holland1975adaptation}.

@@

The encoding for any polynomial will be as follows:
\begin{enumerate}
\item an initial segment detailing which monomials are active (the 1st monomial is always active), this is represented in unary description, i.e., each monomial is identified by a single bit
\item the remaining is split into $m$ sets of bits of equal size, each one representing a monomial
\item each monomial is split into $n$ sets of $d$ size each, i.e., a variable
\item for each variable, the remaining bits give the binary description of the variable degree, i.e., the maximum exponent is given by $2^d-1$
\end{enumerate}

Let's see an example: consider polynomial $x_1^3 x_3 + x_3^7 + x_1 x_2$ with $m = 4, n = 3$ and $d=3$. One possible encoding would be:
$$110 - 011,000,001~~;~~000,000,111~~;~~001,001,000~~;~~110,010,101$$

@@

The first three bits inform that the second and third monomials are active while the fourth is not (as said, the first monomial is always active). This last monomial does not enter neither in the polynomial regression nor in the fitness evaluation. However, it acts as a kind of junk DNA, becoming active when, in a future mutation or crossover, the third bit of the entire sequence flips from 0 to 1.

Let's interpret the first monomial description, $011,000,001$. It is divided by three since $n=3$. The first triple $011$ is the binary description of the exponent of variable $x_1$ which is 3, so the first monomial includes $x_1^3$. The second triple, $000$, means that $x_2$ is not part of the monomial. The third triple $001$ says that variable $x_3$ has exponent $1$, so the first monomial consists of $x_1^3 x_3$. All the remaining sets of nine bits are interpreted the same way and we get the previous polynomial.

Notice that all binary descriptions give rise to valid polynomials. Notice however that this is not a bijective mapping. For each polynomial there are multiple representations. For example, $x_1+x_2$ and $x_2+x_1$ have different representations. The authors considered that more complex mappings in order to force a one to one mapping would impact negatively in the algorithm performance without giving anything in return.

If the coding consists of entirely zeros, by convention, it describes polynomial $x_1$. This has to do with the execution of the polynomial regression that would fail if we interpret it as the zero polynomial. Anyway, for progressive larger  binary descriptions, the chances of getting this zero description decrease exponentially, so it does not impact in any meaningful way in the algorithm's performance.

@@

Somewhat unexpectedly after some experiences it was found that lower values for $\lambda$ sometimes provide better, even if marginal, results. Figure~\ref{Abalone_dataset_lambdas} shows results for the Abalone dataset with ten runs for each $\lambda$, and figure~\ref{Auto-MPG_dataset_lambdas} presents regularization results for the Auto-MPG dataset. The following section Experimental Results includes information about these datasets.

@@

\end{axis}
\end{tikzpicture}

% \includegraphics[height=6cm,width=\textwidth,angle=0]{figures/Abalone_dataset_lambdas.eps}

\caption{Error distribution by regularisation exponent for the Abalone dataset.}\label{Abalone_dataset_lambdas}

@@

\begin{figure}[htb]\begin{center}
\begin{tikzpicture}
\begin{axis}[width=\textwidth,height=6cm,
	boxplot/draw direction=y,
	xtick={1,2,3,4,5,6,7,8,9,10,11,12,13},
	xticklabels={0.70, 0.75, 0.80, 0.85, 0.90, 0.95, 1.00, 1.05, 1.10, 1.15, 1.20, 1.25, 1.30},
	xlabel={regularisation exponent ($\lambda$)},
	ymin=2.0,
	ymax=5.0,
	ylabel={Error distribution (\ac{rmse})},
	title={Error distribution by regularisation exponent (\textbf{Auto-MPG dataset})},
	mark options={scale=0.5},
	]
	\addplot[only marks, mark=o,color=black] table [x expr=1+0.2*rand,y index=0] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=2+0.2*rand,y index=1] {data/lambda.errors.Auto-Mpg.dat};		
	\addplot[only marks, mark=o,color=black] table [x expr=3+0.2*rand,y index=2] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=4+0.2*rand,y index=3] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=5+0.2*rand,y index=4] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=6+0.2*rand,y index=5] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=7+0.2*rand,y index=6] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=8+0.2*rand,y index=7] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=9+0.2*rand,y index=8] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=10+0.2*rand,y index=9] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=11+0.2*rand,y index=10] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=12+0.2*rand,y index=11] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=13+0.2*rand,y index=12] {data/lambda.errors.Auto-Mpg.dat};

	\pgfplotsset{boxplot/every box/.append style={fill=gray!50!white}}
	\addplot[boxplot] table [y index=0] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=1] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=2] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=3] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=4] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=5] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=6] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=7] {data/lambda.errors.Auto-Mpg.dat};		
	\addplot[boxplot] table [y index=8] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=9] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=10] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=11] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=12] {data/lambda.errors.Auto-Mpg.dat};

\end{axis}
\end{tikzpicture}

% \includegraphics[height=6cm,width=\textwidth,angle=0]{figures/Abalone_dataset_lambdas.eps}

\caption{Error distribution by regularisation exponent for the Auto-MPG dataset.}\label{Auto-MPG_dataset_lambdas}

The typical inflection point lies around $\lambda = 0.8$. The following results use the regularisation parameter with this value.

@@

It was used the R package genalg~\cite{willighage2012genalg} for the execution of genetic algorithm. The operators were the standard ones: (a) crossover, i.e., a pair of solutions from the previous generations are combined by splitting and mixing their respective representations, and (b) mutation, changing the values of single bits; the mutation chance applied in the datasets was 5\%. There was also elitism between generations, i.e., 20\% of the best solutions are kept in the next generation.

@@

To compare this paper's proposed algorithm we applied the exact same train and test samples using other learning algorithms, namely: Linear Regression, Support Vector Machines~\cite{Meyer12}, Regression Trees~\cite{Therneau13}, Conditional Inference Trees~\cite{Hothorn06, Strobl07, Strobl08} and Random Forests~\cite{Liaw02}

In order to train and test the performance of \ac{GAPoly} it was used several datasets (see below). For each dataset, we selected 70\% for training purposes and the remaining observations to make a test set in order to compute the estimated \ac{rmse}. To achieve more robust results, each dataset were processed 25 times, each one with different samples for the train and test sets. For the datasets with attribute values of different magnitudes, a preliminary scaling was executed. The results below are boxplots for the test set error predictions over these different runs.

\textbf{Artificial}: this is an artificial dataset with four numeric features, $x_1, \ldots x_4$, where $x_1,x_3$ are outcomes from Poisson random variables, and $x_2,x_4$ from Normal random variables. The dependent variable $y$ is given by expression $x_2x_4^2 + x_1^2x_3 + 5$. The dataset includes 50 observations and, only in this case, there were executed just 10 runs.

\begin{figure}[htb]\begin{center}
\begin{tikzpicture}
\begin{axis}[width=\textwidth,height=6cm,
	boxplot/draw direction=y,
	xtick={1,2,3,4,5,6},
	xticklabels={GA.Poly,Lin.Reg,SVM,RPART,Rnd.For,CI.Tree},
	xlabel={Regression Method},
	ymin=0,
	ymax=300,
	ylabel={Error distribution (\ac{rmse})},
	title={Regression results for \textbf{Artificial dataset}},
	mark options={scale=0.5},
	]
	\addplot[only marks, mark=o,color=black] table [x expr=1+0.2*rand,y index=0] {data/Articial_dataset.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=2+0.2*rand,y index=1] {data/Articial_dataset.dat};		
	\addplot[only marks, mark=o,color=black] table [x expr=3+0.2*rand,y index=2] {data/Articial_dataset.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=4+0.2*rand,y index=3] {data/Articial_dataset.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=5+0.2*rand,y index=4] {data/Articial_dataset.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=6+0.2*rand,y index=5] {data/Articial_dataset.dat};

	\pgfplotsset{boxplot/every box/.append style={fill=gray!50!white}}
	\addplot[boxplot] table [y index=0] {data/Articial_dataset.dat};
	\addplot[boxplot] table [y index=1] {data/Articial_dataset.dat};
	\addplot[boxplot] table [y index=2] {data/Articial_dataset.dat};
	\addplot[boxplot] table [y index=3] {data/Articial_dataset.dat};
	\addplot[boxplot] table [y index=4] {data/Articial_dataset.dat};
	\addplot[boxplot] table [y index=5] {data/Articial_dataset.dat};

\end{axis}
\end{tikzpicture}

% \includegraphics[height=6cm,width=\textwidth,angle=0]{figures/Abalone_dataset_lambdas.eps}

		\caption{results for Artificial dataset}
		\label{artificial_dataset1_lambda1.0}

This dataset was used in order to verify if \ac{GAPoly} was able to find the polynomial relation, which the algorithm did (cf. figure~\ref{artificial_dataset1_lambda1.0}). In this case, we used a population of 100 solutions with 50 iterations for each run.

@@

\textbf{Housing}: This data set concerns the task of predicting housing values in areas of Boston. There are 13 continuous attributes and the dependent variable is the median value of owner-occupied homes in \$1000's\footnote{This and the remaining regression datasets were selected from Luis Torgo's data repository, http://www.dcc.fc.up.pt/~ltorgo/Regression/DataSets.html. Most of these datasets originally come from UCI ML repository, http://archive.ics.uci.edu/ml/}. There are 506 observations. Figure~\ref{Housing_dataset_lambda0.8_25runs} presents the results for this dataset.

\begin{figure}[htb]\begin{center}
\begin{tikzpicture}
\begin{axis}[width=\textwidth,height=6cm,
	boxplot/draw direction=y,
	xtick={1,2,3,4,5,6},
	xticklabels={GA.Poly,Lin.Reg,SVM,RPART,Rnd.For,CI.Tree},
	xlabel={Regression Method},
	ymin=0.25,
	ymax=0.85,
	ylabel={Error distribution (\ac{rmse})},
	title={Regression results for \textbf{Housing dataset}},
	mark options={scale=0.5},
	]
	\addplot[only marks, mark=o,color=black] table [x expr=1+0.2*rand,y index=0] {data/Housing300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=2+0.2*rand,y index=1] {data/Housing300_lambda0.8_25runs.dat};		
	\addplot[only marks, mark=o,color=black] table [x expr=3+0.2*rand,y index=2] {data/Housing300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=4+0.2*rand,y index=3] {data/Housing300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=5+0.2*rand,y index=4] {data/Housing300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=6+0.2*rand,y index=5] {data/Housing300_lambda0.8_25runs.dat};

	\pgfplotsset{boxplot/every box/.append style={fill=gray!50!white}}
	\addplot[boxplot] table [y index=0] {data/Housing300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=1] {data/Housing300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=2] {data/Housing300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=3] {data/Housing300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=4] {data/Housing300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=5] {data/Housing300_lambda0.8_25runs.dat};

\end{axis}
\end{tikzpicture}

% \includegraphics[height=6cm,width=\textwidth,angle=0]{figures/Abalone_dataset_lambdas.eps}

		\caption{results for Boston Housing dataset}
		\label{Housing_dataset_lambda0.8_25runs}

Just as an example of the model the \ac{GAPoly} algorithm outputs: in this dataset the best polynomial was the following:

@@

For comparisation if we access the mean decrease in accuracy found by Random Forests, the most important attributes are -- in decreasing order -- $x_{13}, x_6, x_5$ (but $x_5$ is already considered $4$ times less important than $x_6$). Both algorithms agree in two of their three most important attributes.

@@

\begin{figure}[htb]\begin{center}
\begin{tikzpicture}
\begin{axis}[width=\textwidth,height=6cm,
	boxplot/draw direction=y,
	xtick={1,2,3,4,5,6},
	xticklabels={GA.Poly,Lin.Reg,SVM,RPART,Rnd.For,CI.Tree},
	xlabel={Regression Method},
	ymin=0.64,
	ymax=0.79,
	ylabel={Error distribution (\ac{rmse})},
	title={Regression results for \textbf{Abalone dataset}},
	mark options={scale=0.5},
	]
	\addplot[only marks, mark=o,color=black] table [x expr=1+0.2*rand,y index=0] {data/Abalone300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=2+0.2*rand,y index=1] {data/Abalone300_lambda0.8_25runs.dat};		
	\addplot[only marks, mark=o,color=black] table [x expr=3+0.2*rand,y index=2] {data/Abalone300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=4+0.2*rand,y index=3] {data/Abalone300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=5+0.2*rand,y index=4] {data/Abalone300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=6+0.2*rand,y index=5] {data/Abalone300_lambda0.8_25runs.dat};

	\pgfplotsset{boxplot/every box/.append style={fill=gray!50!white}}
	\addplot[boxplot] table [y index=0] {data/Abalone300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=1] {data/Abalone300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=2] {data/Abalone300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=3] {data/Abalone300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=4] {data/Abalone300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=5] {data/Abalone300_lambda0.8_25runs.dat};

\end{axis}
\end{tikzpicture}

% \includegraphics[height=6cm,width=\textwidth,angle=0]{figures/Abalone_dataset_lambdas.eps}

\caption{results for Abalone dataset} \label{Abalone_dataset_lambda0.8_25runs}

@@

\begin{figure}[htb]\begin{center}
\begin{tikzpicture}
\begin{axis}[width=\textwidth,height=6cm,
	boxplot/draw direction=y,
	xtick={1,2,3,4,5,6},
	xticklabels={GA.Poly,Lin.Reg,SVM,RPART,Rnd.For,CI.Tree},
	xlabel={Regression Method},
	ymin=0.3,
	ymax=0.55,
	ylabel={Error distribution (\ac{rmse})},
	title={Regression results for \textbf{Auto-MPG dataset}},
	mark options={scale=0.5},
	]
	\addplot[only marks, mark=o,color=black] table [x expr=1+0.2*rand,y index=0] {data/Auto-Mpg300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=2+0.2*rand,y index=1] {data/Auto-Mpg300_lambda0.8_25runs.dat};		
	\addplot[only marks, mark=o,color=black] table [x expr=3+0.2*rand,y index=2] {data/Auto-Mpg300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=4+0.2*rand,y index=3] {data/Auto-Mpg300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=5+0.2*rand,y index=4] {data/Auto-Mpg300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=6+0.2*rand,y index=5] {data/Auto-Mpg300_lambda0.8_25runs.dat};

	\pgfplotsset{boxplot/every box/.append style={fill=gray!50!white}}
	\addplot[boxplot] table [y index=0] {data/Auto-Mpg300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=1] {data/Auto-Mpg300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=2] {data/Auto-Mpg300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=3] {data/Auto-Mpg300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=4] {data/Auto-Mpg300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=5] {data/Auto-Mpg300_lambda0.8_25runs.dat};

\end{axis}
\end{tikzpicture}

% \includegraphics[height=6cm,width=\textwidth,angle=0]{figures/Abalone_dataset_lambdas.eps}

\caption{results for Auto-MPG dataset}	\label{Auto-Mpg_dataset_lambda0.8_25runs}

@@

\begin{figure}[htb]\begin{center}
\begin{tikzpicture}
\begin{axis}[width=\textwidth,height=7cm,
	boxplot/draw direction=y,
	xtick={1,2,3,4,5,6},
	xticklabels={GA.Poly,Lin.Reg,SVM,RPART,Rnd.For,CI.Tree},
	xlabel={Regression Method},
	ymin=0.53,
	ymax=0.85,
	ylabel={Error distribution (\ac{rmse})},
	title={Regression results for \textbf{Kinematics dataset}},
	mark options={scale=0.5},
	]
	\addplot[only marks, mark=o,color=black] table [x expr=1+0.2*rand,y index=0] {data/Kinematics300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=2+0.2*rand,y index=1] {data/Kinematics300_lambda0.8_25runs.dat};		
	\addplot[only marks, mark=o,color=black] table [x expr=3+0.2*rand,y index=2] {data/Kinematics300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=4+0.2*rand,y index=3] {data/Kinematics300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=5+0.2*rand,y index=4] {data/Kinematics300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=6+0.2*rand,y index=5] {data/Kinematics300_lambda0.8_25runs.dat};

	\pgfplotsset{boxplot/every box/.append style={fill=gray!50!white}}
	\addplot[boxplot] table [y index=0] {data/Kinematics300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=1] {data/Kinematics300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=2] {data/Kinematics300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=3] {data/Kinematics300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=4] {data/Kinematics300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=5] {data/Kinematics300_lambda0.8_25runs.dat};

\end{axis}
\end{tikzpicture}

\caption{results for Kinematics dataset}
		\label{Kinematics300_lambda0.8_25runs}

@@

The proposed method has competitive results comparing with some well-known regression methods. Only Random Forest outperforms \ac{GAPoly} systematically (it also outperforms all the other regression algorithms). One exception -- the artificial dataset that uses a straightforward polynomial relation -- is the Auto-MPG datatest where \ac{GAPoly} has comparable results. This is evidence that applying standard genetic operators for polynomial model searching is a viable tool for regression purposes.
